|

### 2020-07-15 paper.Rmd
Removed code example.

1. Center the 2-dimensional matrix $\mathbf{Y}$ and compute its polar coordinate representation $(r, \theta)$.
2. For each observation, first use Eq. \ref{eq:cutR} to ensure the radius $r$ is within the specified range, and then apply the radial transformation defined in Eq. \ref{eq:resc} to obtain $r'$.
3. Use the transformed radial coordinate $r'$ to re-compute the mapping onto Euclidean coordinates $(x, y)$.
4. To fit the final projection onto the plotting canvas ranging between $[-1,1]$, we rescale each observation by $0.9 \cdot \mathrm{half\_range}$.

XXX mention function, but full code should be in documentation

 This display has two important new input parameters, the scaling `s` for computing $p_{eff}$, and the overall scale `R`. Both these parameters are described in Section \ref{sec:params} above.

Note that the ratio of the `tourr` parameter `half_range` and the new parameter `R` set the scale for fitting the displayed data on the plotting canvas ranging between $[-1,1]$. With the default settings `half_range` = `R` and we apply a scaling factor $0.9$ to contain the projected points within the display.

Below we show example code demonstrates how the new display redistributes the projected points drawn uniformly inside a 5D hypersphere.
```{r codeExampel, echo=TRUE, eval=FALSE}
# use geozoo to uniformly generate points inside a 5D sphere
sphere5 <- geozoo::sphere.solid.random(5)$points
colnames(sphere5) <- c("x1", "x2", "x3", "x4", "x5") # naming variables
# standard tour animation with default settings
animate_xy(sphere5)
# new sage display to redistribute the points based on projected volume
animate_sage(sphere5)
# we can use R and s to tune the display
# for example use R to zoom in near the center
# we also adjust half_range to fit the display on the plotting canvas
animate_sage(sphere5, R = 0.1, half_range = 0.1)
```

>>>>

1. Center the 2-dimensional matrix $\mathbf{Y}$ and compute its polar coordinate representation $(r, \theta)$.
2. For each observation, first use Eq. \ref{eq:cutR} to ensure the radius $r$ is within the specified range, and then apply the radial transformation defined in Eq. \ref{eq:resc} to obtain $r'$.
3. Use the transformed radial coordinate $r'$ to re-compute the mapping onto Euclidean coordinates $(x, y)$.
4. To fit the final projection onto the plotting canvas ranging between $[-1,1]$, we rescale each observation by $0.9 \mathrm{half\_range}$.

The display can be added when calling the `animate` function in `tourr`, as

```{r codeExample, echo=TRUE, eval=FALSE}
tourr::animate(data, tour_path, display=display_sage(s, R, half_range))
```

and introduces the scaling parameter `s` for computing $p_{eff}$, and the overall scale `R` used for trimming. Both these parameters are described in Section \ref{sec:params} above. The ratio of `half_range` and `R` set the scale for fitting the displayed data on the plotting canvas, by default `half_range` = `R` and we apply the scaling factor $0.9$ to contain the projected points within the display.
